Next Trippy Structures\thanks{Supported by organization x.}

### 2019-06-10 paper.tex
Update on Overleaf.

\subsection{Query performance}
\label{sec:time}
Missing a comparison of \acumm~vs \ttctr!

We have implemented the most adequate queries for \ttctr~and \ctr~from those described in Section~\ref{sec:rq}, and measured their average execution time from 100.000 randomly generated queries on a Intel Xeon E5-2620v4@2.1 GHz machine. In this section we will only discuss four of the possible configurations tested for both \ttctr~and \ctr, with t$_{\Psi}$ values of 32 and 512 combining with \texttt{WM} using either uncompressed bitvectors (\texttt{RG32}) or the most compressed (\texttt{RRR128}). These four configurations should be illustrative enough to provide an understanding of the space-time trade-offs of our approaches, although the execution times for all tested configurations can be found in the Appendix A.

>>>>

\subsection{Query performance}
\label{sec:time}
We have implemented the most adequate queries for \ttctr~and \ctr~from those described in Section~\ref{sec:rq}, and measured their average execution time from 100.000 randomly generated queries on a Intel Xeon E5-2620v4@2.1 GHz machine. In this section we will only discuss four of the possible configurations tested for both \ttctr~and \ctr, with t$_{\Psi}$ values of 32 and 512 combining with \texttt{WM} using either uncompressed bitvectors (\texttt{RG32}) or the most compressed (\texttt{RRR128}). These four configurations should be illustrative enough to provide an understanding of the space-time trade-offs of our approaches, although the execution times for all tested configurations can be found in the Appendix A.
